\title{Einführung in die grammatische Beschreibung des Deutschen}
\subtitle{}
\BackTitle{Einführung in die grammatische Beschreibung des Deutschen}
\BackBody{\begin{sloppypar}
\textit{Einführung in die grammatische Beschreibung des Deutschen} ist eine Einführung in die deskriptive Grammatik am Beispiel des gegenwärtigen Deutschen in den Bereichen Phonetik, Phonologie, Morphologie, Syntax und Graphematik.
Das Buch ist für jeden geeignet, der sich für die Grammatik des Deutschen interessiert, vor allem aber für Studierende der Germanistik bzw.\ Deutschen Philologie.
Im Vordergrund steht die Vermittlung grammatischer Erkenntnisprozesse und Argumentationsweisen auf Basis konkreten sprachlichen Materials.
Es wird kein spezieller theoretischer Rahmen angenommen, aber nach der Lektüre sollten Leser in der Lage sein, sowohl deskriptiv ausgerichtete Forschungsartikel als auch theorienahe Einführungen lesen zu können.
Trotz seiner Länge ist das Buch für den Unterricht in BA-Studiengängen geeignet, da grundlegende und fortgeschrittene Anteile getrennt werden und die fünf Teile des Buches auch einzeln verwendet werden können.
Das Buch enthält zahlreiche Übungsaufgaben, die im Anhang gelöst werden.

<<<<<<< HEAD
\vspace{1\baselineskip}

\textbf{Roland Schäfer} studierte Sprachwissenschaft und Japanologie an der Philipps-Universität Marburg.
Er war wissenschaftlicher Mitarbeiter an der Georg-August Universität Göttingen und der Freien Universität Berlin.
Er promovierte 2008 an der Georg-August Universität Göttingen mit einer theoretischen Arbeit zur Syntax-Semantik-Schnittstelle.
Seine aktuellen Forschungsschwerpunkte sind die korpusbasierte Morphosyntax und Graphematik des Deutschen und anderer germanischer Sprachen sowie die Erstellung sehr großer Korpora aus Webdaten.
Seit 2015 leitet er das DFG-finanzierte Projekt \textit{Linguistische Web-Charakterisierung und Webkorpuserstellung} an der Freien Universität Berlin.
Er hat langjährige Lehrerfahrung in deutscher und englischer Sprachwissenschaft sowie theoretischer Sprachwissenschaft und Computerlinguistik.
\end{sloppypar}}
\dedication{Für Mausi und so.}
\typesetter{Roland Schäfer}
\proofreader{Thea Dittrich}
\author{Roland Schäfer}
\newlength{\csspine} 
\newlength{\bodspine}
\setlength{\csspine}{27.0559784mm} % Please calculate: Total Page Number (excluding cover, usually (Total Page - 3)) * 0.0572008 mm
\setlength{\bodspine}{40mm} % Please calculate: Total Page Number (excluding cover) * BODFACTOR + BODABS
\definecolor{lsYellow}{cmyk}{0,0.25,1,0}
\newcommand{\lsSeriesColor}{lsYellow}
\newcommand{\lsSeriesTitle}{Textbooks in Language Sciences~2}
\renewcommand{\lsISBN}{978-3-944675-53-4}                     
\renewcommand{\lsSeries}{tbls} % use lowercase acronym, e.g. sidl, eotms, tgdi
\renewcommand{\lsSeriesNumber}{2} %will be assigned when the book enters the proofreading stage
\renewcommand{\lsURL}{http://langsci-press.org/catalog/book/46} % contact the coordinator for the right number
=======
\title{The Alor-Pantar languages}  %look no further, you can change those things right here.
\subtitle{History and typology}
\BackTitle{The Alor-Pantar languages} % Change if BackTitle != Title
\BackBody{The Alor-Pantar family constitutes the westernmost outlier group of Papuan (Non-Austronesian) languages. Its twenty or so languages are spoken on the islands of Alor and Pantar, located just north of Timor, in eastern Indonesia. Together with the Papuan languages of Timor, they make up the Timor-Alor-Pantar family. The languages average 5,000 speakers and are under pressure from the local Malay variety as well as the national language, Indonesian. 
 
This volume studies the internal and external linguistic history of this interesting group, and showcases some of its unique typological features, such as the preference to index the transitive patient-like argument on the verb but not the agent-like one; the extreme variety in morphological alignment patterns; the use of plural number words; the existence of quinary numeral systems; the elaborate spatial deictic systems involving an elevation component; and the great variation exhibited in their kinship systems.
 
Unlike many other Papuan languages, Alor-Pantar languages do not exhibit clause-chaining, do not have switch reference systems, never suffix subject indexes to verbs, do not mark gender, but do encode clusivity in their pronominal systems. Indeed, apart from a broadly similar head-final syntactic profile, there is little else that the Alor-Pantar languages share with Papuan languages spoken in other regions. While all of them show some traces of contact with Austronesian languages, in general, borrowing from Austronesian has not been intense, and contact with Malay and Indonesian is a relatively recent phenomenon in most of the Alor-Pantar region.}
%\dedication{Change dedication in localmetadata.tex}
%\typesetter{Change typesetter in localmetadata.tex}
%\proofreader{Change proofreaders in localmetadata.tex}
\author{Marian Klamer}

\renewcommand{\lsISBN}{978-3-944675-49-7}                     
\renewcommand{\lsSeries}{sidl} % use lowercase acronym, e.g. sidl, eotms, tgdi
\renewcommand{\lsSeriesNumber}{3} %will be assigned when the book enters the proofreading stage
\renewcommand{\lsURL}{http://langsci-press.org/catalog/book/66} % contact the coordinator for the right number
>>>>>>> 80a0aedee630d0af986810f7937fedb206a22233
